---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# jl12: Johnson-Laird's (2012) Tonal Dissonance Model

[![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![Travis build status](https://travis-ci.org/pmcharrison/jl12.svg?branch=master)](https://travis-ci.org/pmcharrison/jl12)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/pmcharrison/jl12?branch=master&svg=true)](https://ci.appveyor.com/project/pmcharrison/jl12)
[![Coverage status](https://coveralls.io/repos/github/pmcharrison/jl12/badge.svg)](https://coveralls.io/r/pmcharrison/jl12?branch=master)

The `jl12` R package implements Johnson-Laird's (2012) tonal dissonance model.

## Installation

Within R, you can install the current version of `jl12` from Github as follows:

``` r
if (!require(devtools)) install.packages("devtools")
devtools::install_github("jl12")
```

## Usage

Higher scores correspond to greater dissonance. 
These scores correspond to each of the distinguishable categories
in the cultural component of Johnson-Laird et al.'s (2012) algorithm.

Major chord:

```{r}
library(jl12)
jl_tonal_dissonance(c(0, 4, 7))
```

Minor chord:

```{r}
jl_tonal_dissonance(c(0, 3, 7))
```

Cluster chord:

```{r}
jl_tonal_dissonance(c(0, 1, 2))
```

The model comprises several rules. 
It is possible to call these rules individually, for example:

```{r}
jl_rule_1(c(0, 3, 7))
jl_rule_2(c(0, 3, 7))
jl_rule_3(c(0, 3, 7))
```

## References

Johnson-Laird, P. N., Kang, O. E., & Leong, Y. C. (2012). On musical dissonance. Music Perception, 30(1), 19–35.
